Cell Decompositions for Rank Two Quiver Grassmannians

### 2018-03-11 Grassmannian_cells.tex
Some intro edits

In Section \ref{sec:combinatorics}, we reveal the combinatorics behind the obtained cell decompositions introducing the notion of $2$-quivers which is a slight generalization of the notion of usual quivers.
Theorem \ref{thm:2quivercells} can be formulated as follows.
\begin{thm}
  With every truncated preprojective representation $P_{m+1}^V$, say with $\dim V=r$, we can associated a $2$-quiver $\mathcal Q_{m+1}^{[r]}$ such that the cells of the cell decomposition attached to $\Gr_\bfe(P_{m+1}^V)$ are labeled by strong successor closed subsets $\beta\subset (\mathcal Q_{m+1}^{[r]})_0$.
  In particular, the Euler characteristic $\chi(\Gr_\bfe(P_{m+1}^V))$ is given by the number of these subsets.
\end{thm}
\sayD{I need to include a conjecture about the dimensions of cells coming from the combinatorial construction of counting/Poincare polynomials}
\sayT{Insert something about Dyck path combinatorics and the correspondence here}
\sayT{maybe we can erase some parts which show up twice in the introduction?}

>>>>

In Section \ref{sec:combinatorics}, we reveal the combinatorics behind the obtained cell decompositions introducing the notion of $2$-quivers which is a slight generalization of the notion of usual quivers.
Theorem \ref{thm:2quivercells} can be formulated as follows.
\begin{thm}
  With every truncated preprojective representation $P_{m+1}^V$, say with $\dim V=r$, we can associated a $2$-quiver $\mathcal Q_{m+1}^{[r]}$ such that the cells of the cell decomposition attached to $\Gr_\bfe(P_{m+1}^V)$ are labeled by strong successor closed subsets $\beta\subset (\mathcal Q_{m+1}^{[r]})_0$.
  In particular, the Euler characteristic $\chi(\Gr_\bfe(P_{m+1}^V))$ is given by the number of these subsets.
\end{thm}

The results of \cite{rupel} giving a combinatorial construction of counting polynomials for quiver Grassmannians of preprojective/preinjective representations of generalized Kronecker quivers $K(n)$ suggest the following.
\begin{conjecture}
  There exists a torus action on $\Gr_\bfe(P_{m+1}^V)$ such that the affine cell corresponding to a compatible pair $(S_H,S_V)$ has dimension...
\end{conjecture}
\sayD{I need to include a conjecture about the dimensions of cells coming from the combinatorial construction of counting/Poincare polynomials}
\sayT{Insert something about Dyck path combinatorics and the correspondence here}
\sayT{maybe we can erase some parts which show up twice in the introduction?}
